### 2022-09-26 paper/200-base-language.tex
A little writing

To type-check the base language, we need to scope graphs. This section describes how scope graphs are used.

@@

These are all the definitions we will need to type-check programs.

>>>>

To type-check the base language, we need to scope graph, this section describes how scope graphs are used.

@@

These are all the definitions we will need to type-check programs. Next, we will introduce some Statix relations that can be used to interact with these scope graphs:

\begin{lstlisting}
scopePutType : scope * ID * Expr -> scope
scopePutSubst : scope * ID * (scope * Expr) -> scope
scopeGetName : scope * ID -> (NameEntry * scope)
scopeGetNames : scope * ID -> list((path * (ID * NameEntry)))
empty_scope : -> scopes
\end{lstlisting}
